---
title: "Infographics_2023"
output: "github_document"
date: "2026-01-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#This project is a step by step process to getting U.S. Census data,
#accompanying boundary files, displaying them geographically, and
#creating #visualizations for CENTRO published infographics.


#We will start by calling the necesarry libraries to perform all
#operations. 

```{r Call libraries, warning=FALSE, message=FALSE}
#We first install the package {pacman} if necessary. This package allows the 
#user to load and install packages in a more streamlined manner.

if (!require("pacman")) install.packages("pacman")

pacman::p_load(tidyverse,       #Tidyverse for data manipulation.
               tidycensus,      #To handle Census data.
               sf,              #To handle spatial data.
               tmap,            #To visualize spatial data.
               leaflet,         #in case we wanted to do interactive maps
               stringr)         #To do some string manipulation.

#We are also going to give the program the instruction to avoid using scientific
#notation when generating calculations.
options(scipen=999)
```

#The first step in our analysis is gathering the data we need to produce the 
#visualizations.

#In 2023, there were 15 states for wich Puerto Rican population data was
#available based on the 65k threshhold the U.S. Census establishes for reporting
#information. These were: California, Connecticut, Florida, Georgia, Illinois,
#Massachusetts, Maryland, New Jersey, New York, North Carolina, Ohio, 
#Pennsylvania, Texas, Virginia, adn Wisconsin. 

#We will use the "get_acs" function from the {tydcensus} package to get Puerto 
#Rican population data for each of the states listed above. Additionally we will
#gather information on the Hispanic population since we will also be visualazing
#this group in a select number of states. 

```{r PR pop by county by state, message=FALSE, warning=FALSE, results='hide'}

#First we create a list containing the abbreviations of all the states of
#interest. This will serve for us to loop through and create new data frames 
#for each state. 
st_abv <- list("CA","CT","FL","GA","IL","MA","MD","NJ","NY",
               "NC","OH","PA","TX","VA","WI")

#Getting data for all 15 states. 
for (abv in st_abv) {
  
  df_current <- get_acs(geography = "county",
                    variables = c(
                      hisp_pop = "B03001_003E",
                      pr_pop = "B03001_005E"
                    ),
                    state = abv,
                    year = 2023,
                    survey = "acs5",output = "wide",
                    geometry = TRUE,
                    progress_bar = FALSE) %>% 
    select(-ends_with("M")) %>%     #This command deletes the margins of error.
    mutate(pct_prpop = pr_pop/sum(pr_pop)*100,
           pct_hispop = hisp_pop/sum(hisp_pop)*100,
           sub_name = str_replace(NAME, " County.*$",""))

#Here we name the data frame being created with the associated state.  
df_name <- paste0("df_", abv)
assign(df_name, df_current)
}

```

#We are also interested in generating visualizations for the Puerto Rican
#population in selected cities across the U.S.. Because we are using data at the 
#tract level and bounding them to counties that constitute the desired cities, 
#we will generate the data frames for these cities separately. 

```{r PR pop by census tract by selected cities, message=FALSE, warning=FALSE}

#NYC
df_nyc <- get_acs(geography = "tract",
                  variables = c(
                      hisp_pop = "B03001_003E",
                      pr_pop = "B03001_005E"
                    ),
                  state = "NY",
                  county = c("New York","Bronx","Kings","Richmond","Queens"),
                  year = 2023,
                  survey = "acs5",
                  output = "wide",
                  geometry = TRUE,
                  progress_bar = FALSE) %>%
  select(-ends_with("M")) %>%
  mutate(pct_prpop = pr_pop/sum(pr_pop)*100,
         pct_hispop = hisp_pop/sum(hisp_pop)*100,
         sub_name = str_replace(NAME, " County.*$",""))

#Philadelphia
df_phl <-  get_acs(geography = "tract",
                  variables = c(
                      hisp_pop = "B03001_003E",
                      pr_pop = "B03001_005E"
                    ),
                  state = "PA",
                  county = "Philadelphia",
                  year = 2023,
                  survey = "acs5",
                  output = "wide",
                  geometry = TRUE,
                  progress_bar = FALSE) %>%
  select(-ends_with("M")) %>%
  mutate(pct_prpop = pr_pop/sum(pr_pop)*100,
         pct_hispop = hisp_pop/sum(hisp_pop)*100,
         sub_name = str_replace(NAME, " County.*$",""))

#Chicago

```

#Finaly, we will generate similar datasets for the whole U.S. at the state level.

```{r PR pop for US by state, message=FALSE, warning=FALSE}
df_us <- get_acs(geography = "state",
                  variables = c(
                      hisp_pop = "B03001_003E",
                      pr_pop = "B03001_005E"
                    ),
                  year = 2023,
                  survey = "acs5",
                  output = "wide",
                  geometry = TRUE,
                  progress_bar = FALSE) %>%
  select(-ends_with("M")) %>%
  mutate(pct_prpop = pr_pop/sum(pr_pop)*100,
         pct_hispop = hisp_pop/sum(hisp_pop)*100,
         sub_name = str_replace(NAME, " County.*$",""))
```

#After we have genereted our data, we can proceed with visualizing them 
#geographically. 

#We can quickly glance at our data  by using the plot() function. 
```{r Map at a glance, message=FALSE, warning=FALSE}
#For example, we can quickly see the distribution of Puerto Rican population in 
#NY state. 
plot(df_NY["pct_prpop"])

#This map shows, rather poorly, that Puerto Ricans are concentrated in the NYC
#and surrounding areas, with some presence in counties with large cities, such 
#as Buffalo and Rochester.
```

#We can now procede to develop a more nuanced structure that produces maps that 
#are both informative and visually appeasing. 

#But first we should look at the basic structures of our spatial data. 
```{r Spatial structure, warning=FALSE, message=FALSE}
#Because all our data sets were downloaded in the same manner, we can expect them
#to have similar structures. Of particular interest to us right now is their 
#projections. 

#Sticking with NY, we can look at the basic structure of the spatial data frame
#using the str() function.
str(df_NY)
#This provides us with a basic description of the contents of the data frame. We
#can see from the results that all variables have correct types. But we do not 
#see the projection information. To get that information we will use the 
#st_cr() function.
print(st_crs(df_NY)$epsg)
print(st_crs(df_NY)$wkt)
#Both instructions provide the EPSG code for the current coordinate system and 
#the name of the current coordinate system. For now we will not make any changes. 
```

#With a basic understanding of our datasets, we will proceed with visualizing
#them. 

```{r}
ctr_plt <- c("#dde8eb", "#bbd1d7", "#8eb2bc", "#637d84", "#39474b")

curr_map = tm_shape(df_CA) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1.5,
                                                 item.width = 3,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_labels_highlighted("sub_name",
                      size = 0.65,
                      col = "white",
                      fontface = 2,
                      bgcol = "black",
                      options = opt_tm_text(remove_overlap = TRUE,
                                            bg.padding = 0))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"test.png")
```

































