---
title: "Infographics_2023"
output: "github_document"
date: "2026-01-22"
editor_options: 
  markdown: 
    wrap: 100
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#This project is a step by step process to getting U.S. Census data, #accompanying boundary files,
#displaying them geographically, and #creating #visualizations for CENTRO published infographics.

#We will start by calling the necesarry libraries to perform all #operations.

```{r Call libraries, warning=FALSE, message=FALSE}
#We first install the package {pacman} if necessary. This package allows the 
#user to load and install packages in a more streamlined manner.

if (!require("pacman")) install.packages("pacman")

pacman::p_load(tidyverse,       #Tidyverse for data manipulation.
               tidycensus,      #To handle Census data.
               sf,              #To handle spatial data.
               tmap,            #To visualize spatial data.
               leaflet,         #in case we wanted to do interactive maps
               stringr,         #To do some string manipulation.
               tigris,          #To do some spatial data manipulation.
               grid)            #To do some visualization

#We are also going to give the program the instruction to avoid using scientific
#notation when generating calculations.
options(scipen=999)
```

#The first step in our analysis is gathering the data we need to produce the #visualizations.

#In 2023, there were 15 states for wich Puerto Rican population data was #available based on the 65k
#threshhold the U.S. Census establishes for reporting #information. These were: California,
#Connecticut, Florida, Georgia, Illinois, #Massachusetts, Maryland, New Jersey, New York, North
#Carolina, Ohio, #Pennsylvania, Texas, Virginia, adn Wisconsin.

#We will use the "get_acs" function from the {tydcensus} package to get Puerto #Rican population
#data for each of the states listed above. Additionally we will #gather information on the Hispanic
#population since we will also be visualazing #this group in a select number of states.

```{r PR pop by county by state, message=FALSE, warning=FALSE, results='hide'}

#First we create a list containing the abbreviations of all the states of
#interest. This will serve for us to loop through and create new data frames 
#for each state. 
st_abv <- list("CA","CT","FL","GA","IL","MA","MD","NJ","NY",
               "NC","OH","PA","TX","VA","WI")

#Getting data for all 15 states. 
for (abv in st_abv) {
  
  df_current <- get_acs(geography = "county",
                    variables = c(
                      hisp_pop = "B03001_003E",
                      pr_pop = "B03001_005E"
                    ),
                    state = abv,
                    year = 2023,
                    survey = "acs5",output = "wide",
                    geometry = TRUE,
                    progress_bar = FALSE) %>% 
    select(-ends_with("M")) %>%     #This command deletes the margins of error.
    mutate(pct_prpop = pr_pop/sum(pr_pop)*100,
           pct_hispop = hisp_pop/sum(hisp_pop)*100,
           sub_name = str_replace(NAME, " County.*$",""))

#Here we name the data frame being created with the associated state.  
df_name <- paste0("df_", abv)
assign(df_name, df_current)
}

```

#In the previous chunk, we obtained data for the PR adn Hispanic population for
#selected states. In the code, lines were included to clean the names of the 
#counties to ease readability when inserting labels into future visualizations.
#This works relatively well for all states except Connecticut, who switched from 
#its 8 historic counties to 9 "planning regions". We need to do some extra steps
#to clean the names in this state. 
```{r}
#We will use a similar structure to replace the "Planning Region, Connecticut"
#string in the name within the newly created sub_name variable. 
df_CT$sub_name <- str_replace(df_CT$NAME, " Planning.*$","")

#Now we will be able to place county equivalent labels to our visualizations
#for the state of Connecticut. 
```


#We are also interested in generating visualizations for the Puerto Rican #population in selected
#cities across the U.S.. Because we are using data at the #tract level and bounding them to counties
#that constitute the desired cities, #we will generate the data frames for these cities separately.

```{r PR pop by census tract by selected cities, message=FALSE, warning=FALSE}

#NYC
df_nyc <- get_acs(geography = "tract",
                  variables = c(
                      hisp_pop = "B03001_003E",
                      pr_pop = "B03001_005E"
                    ),
                  state = "NY",
                  county = c("New York","Bronx","Kings","Richmond","Queens"),
                  year = 2023,
                  survey = "acs5",
                  output = "wide",
                  geometry = TRUE,
                  progress_bar = FALSE) %>%
  select(-ends_with("M")) %>%
  mutate(pct_prpop = pr_pop/sum(pr_pop)*100,
         pct_hispop = hisp_pop/sum(hisp_pop)*100,
         sub_name = str_replace(NAME, " County.*$",""))

#Philadelphia
df_phl <-  get_acs(geography = "tract",
                  variables = c(
                      hisp_pop = "B03001_003E",
                      pr_pop = "B03001_005E"
                    ),
                  state = "PA",
                  county = "Philadelphia",
                  year = 2023,
                  survey = "acs5",
                  output = "wide",
                  geometry = TRUE,
                  progress_bar = FALSE) %>%
  select(-ends_with("M")) %>%
  mutate(pct_prpop = pr_pop/sum(pr_pop)*100,
         pct_hispop = hisp_pop/sum(hisp_pop)*100,
         sub_name = str_replace(NAME, " County.*$",""))

#Chicago

```

#Finaly, we will generate similar datasets for the whole U.S. at the state level.

```{r PR pop for US by state, message=FALSE, warning=FALSE}
df_us <- get_acs(geography = "state",
                  variables = c(
                      hisp_pop = "B03001_003E",
                      pr_pop = "B03001_005E"
                    ),
                  year = 2023,
                  survey = "acs5",
                  output = "wide",
                  geometry = TRUE,
                  progress_bar = FALSE) %>%
  select(-ends_with("M")) %>%
  mutate(pct_prpop = pr_pop/sum(pr_pop)*100,
         pct_hispop = hisp_pop/sum(hisp_pop)*100,
         sub_name = str_replace(NAME, " County.*$",""))
```

#After we have genereted our data, we can proceed with visualizing them #geographically.

#We can quickly glance at our data by using the plot() function.

```{r Map at a glance, message=FALSE, warning=FALSE}
#For example, we can quickly see the distribution of Puerto Rican population in 
#NY state. 
plot(df_NY["pct_prpop"])

#This map shows, rather poorly, that Puerto Ricans are concentrated in the NYC
#and surrounding areas, with some presence in counties with large cities, such 
#as Buffalo and Rochester.
```

#We can now procede to develop a more nuanced structure that produces maps that #are both
#informative and visually appeasing.

#But first we should look at the basic structures of our spatial data.

```{r Spatial structure, warning=FALSE, message=FALSE}
#Because all our data sets were downloaded in the same manner, we can expect them
#to have similar structures. Of particular interest to us right now is their 
#projections. 

#Sticking with NY, we can look at the basic structure of the spatial data frame
#using the str() function.
str(df_NY)
#This provides us with a basic description of the contents of the data frame. We
#can see from the results that all variables have correct types. But we do not 
#see the projection information. To get that information we will use the 
#st_cr() function.
print(st_crs(df_NY)$epsg)
print(st_crs(df_NY)$wkt)
#Both instructions provide the EPSG code for the current coordinate system and 
#the name of the current coordinate system. For now we will not make any changes. 
```


#With a basic understanding of our datasets, we will proceed with visualizing 
#them.
#We are creating maps of each of the states and cities for which we have
#generated information for both the Puerto Rican and Hispanic populations. 


#Here we set up the color palett that we will bes using to fill the maps.
```{r Centro Data Hub Color Palett, warning=FALSE, message=FALSE}
ctr_plt <- c("#dde8eb", "#bbd1d7", "#8eb2bc", "#637d84", "#39474b")

```

###CALIFORNIA###

```{r California PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_CA) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"CA_pct_prpop.png")
```

```{r California Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_CA) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"CA_pct_hispop.png")
```

###Connecticut###

```{r Connecticut PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_CT) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 0.7,
                                                 item.width = 1.4,
                                                 position = tm_pos_in("right","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"CT_pct_prpop.png")
```

```{r Connecticut Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_CT) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 1.4,
                                                 position = tm_pos_in("right","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"CT_pct_hispop.png")
```

###FLORIDA###

```{r Florida PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_FL) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"FL_pct_prpop.png")
```

```{r Florida Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_FL) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"FL_pct_hispop.png")
```

###GEORGIA###

```{r Georgia PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_GA) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("right","top"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"GA_pct_prpop.png")
```

```{r Georgia Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_GA) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("right","top"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"GA_pct_hispop.png")
```

###ILLINOIS###

```{r Illinois PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_IL) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"IL_pct_prpop.png")
```

```{r Illinois Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_IL) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of \nHispanics by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"IL_pct_hispop.png")
```

###MASSACHUSETTS###

```{r Massachusetts PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_MA) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("center","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"MA_pct_prpop.png")
```

```{r Massachusetts Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_MA) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("center","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"MA_pct_hispop.png")
```

###MARYLAND###

```{r Maryland PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_MD) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("center","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"MD_pct_prpop.png")
```

```{r Maryland Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_MD) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("center","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"MD_pct_hispop.png")
```

###NORTH CAROLINA###

```{r North Carolina PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_NC) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"NC_pct_prpop.png")
```

```{r North Carolina Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_NC) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"NC_pct_hispop.png")
```

###NEW JERSEY###

```{r New Jersey PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_NJ) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("right","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"NJ_pct_prpop.png")
```

```{r New Jersey Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_NJ) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("right","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"NJ_pct_hispop.png")
```

###NEW YORK###

```{r NYC County Map, message=FALSE,warning=FALSE}
df_county_nyc <- df_NY %>% 
  filter(sub_name == "New York" |
         sub_name == "Queens" |
         sub_name == "Kings" |
         sub_name == "Richmond" |
         sub_name == "Bronx") |
         sub_name == "Nassau"
```


```{r New York PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_NY) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

nyc_cnty_map <- tm_shape(df_county_nyc) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt),
                         fill.legend = tm_legend_hide()) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = T,
                      inner.margins = c(0.02,0.17,0.02,0.17)) 
curr_map <- curr_map +
  tm_inset(nyc_cnty_map, 
           group_id = 1,
           width = 11,
           height = 13) +
  tm_components(1, position = c(0.7,0.7))

tmap_save(curr_map, "test.png")

# tmap_save(curr_map,insets_tm = nyc_cnty_map,
#           insets_vp = viewport(x=.88, y=0.5, width = 0.2, height = 0.3),
#           "NY_pct_prpop.png")
```

```{r New York Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_NY) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = F,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = F,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = F,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = F,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"NY_pct_hispop.png")
```

###NEW YORK CITY###

```{r New York City PR, message=FALSE, warning=FALSE}

curr_map <- tm_shape(df_nyc) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)) #+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = -0.03,
            #                                 shadow.offset.y = 0.03))+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = 0.035,
            #                                 shadow.offset.y = -0.035))+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = -0.035,
            #                                 shadow.offset.y = -0.035))+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = 0.035,
            #                                 shadow.offset.y = 0.035))+
            # tm_layout(frame = FALSE,
            #           inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"NYC_pct_prpop.png")
```

```{r New York City Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_nyc) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)) #+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = -0.03,
            #                                 shadow.offset.y = 0.03))+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = 0.035,
            #                                 shadow.offset.y = -0.035))+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = -0.035,
            #                                 shadow.offset.y = -0.035))+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = 0.035,
            #                                 shadow.offset.y = 0.035))+
            # tm_layout(frame = FALSE,
            #           inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"NYC_pct_hispop.png")
```

###OHIO###

```{r Ohio PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_OH) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("right","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"OH_pct_prpop.png")
```

```{r Ohio Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_OH) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("right","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"OH_pct_hispop.png")
```

###PENSYLVANIA###

```{r Pensylvania PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_PA) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"PA_pct_prpop.png")
```

```{r Pensylvania Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_PA) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"PA_pct_hispop.png")
```

###PHILADELPHIA###

```{r Philadelphia PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_phl) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)) #+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = -0.03,
            #                                 shadow.offset.y = 0.03))+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = 0.035,
            #                                 shadow.offset.y = -0.035))+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = -0.035,
            #                                 shadow.offset.y = -0.035))+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = 0.035,
            #                                 shadow.offset.y = 0.035))+
            # tm_layout(frame = FALSE,
            #           inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"PHL_pct_prpop.png")
```

```{r Philadelphia Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_phl) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)) #+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = -0.03,
            #                                 shadow.offset.y = 0.03))+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = 0.035,
            #                                 shadow.offset.y = -0.035))+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = -0.035,
            #                                 shadow.offset.y = -0.035))+
            # tm_text("sub_name",
            #           size = 0.55,
            #           col = "white",
            #           fontface = 2,
            #           options = opt_tm_text(remove_overlap = TRUE,
            #                                 shadow = TRUE,
            #                                 shadow.offset.x = 0.035,
            #                                 shadow.offset.y = 0.035))+
            # tm_layout(frame = FALSE,
            #           inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"PHL_pct_hispop.png")
```

###TEXAS###

```{r Texas PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_TX) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"TX_pct_prpop.png")
```

```{r Texas Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_TX) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"TX_pct_hispop.png")
```

###VIRGINIA###

```{r Virginia PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_VA) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("right","top"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"VA_pct_prpop.png")
```

```{r Virginia Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_VA) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("right","top"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"VA_pct_hispop.png")
```

###WISCONSIN###

```{r Wisconsin PR, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_WI) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"WI_pct_prpop.png")
```

```{r Wisconsin Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(df_WI) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Hispanics\nby County*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","bottom"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"WI_pct_hispop.png")
```

###USA###

```{r USA map wrangling, message=FALSE, warning=FALSE}
#For this exercise, we do not need Puerto Rico in the map. 
#We will remove it. 
df_us <- df_us %>% 
  filter(NAME != "Puerto Rico")

```


```{r USA PR, message=FALSE, warning=FALSE}
#We will use the shift_geometry() function from the {tigris} package, which 
#repositions objects in the map to the "standard" form for inset maps. 
us_shifted <- shift_geometry(df_us)
curr_map <- tm_shape(us_shifted) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_prpop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of Puerto\nRicans by State*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","center"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"usa_pct_prpop.png")
```

```{r USA Hisp, message=FALSE, warning=FALSE}
curr_map <- tm_shape(us_shifted) +
             tm_polygons(lwd = 0.4,
                         col="black",
                         fill = "pct_hispop",
                         fill.scale = tm_scale_intervals(style = "jenks",
                                                         values = ctr_plt,
                         label.format = tm_label_format(digits = 1, 
                                                        suffix = " %",
                                                        text.separator = "to")),
                         fill.legend = tm_legend(title = "Distribution of \nHispanics by State*",
                                                 title.fontface = 2,
                                                 title.fontfamily = "sans",
                                                 item.shape = "square",
                                                 item.height = 1,
                                                 item.width = 2,
                                                 position = tm_pos_in("left","center"),
                                                 frame = FALSE,
                                                 text.size = 0.8,
                                                 title.size = 1)
                           ) +
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.03,
                                            shadow.offset.y = 0.03))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = -0.035,
                                            shadow.offset.y = -0.035))+
            tm_text("sub_name",
                      size = 0.55,
                      col = "white",
                      fontface = 2,
                      options = opt_tm_text(remove_overlap = TRUE,
                                            shadow = TRUE,
                                            shadow.offset.x = 0.035,
                                            shadow.offset.y = 0.035))+
            tm_layout(frame = FALSE,
                      inner.margins = c(0.02,0.17,0.02,0.17))

tmap_save(curr_map,"usa_pct_hispop.png")
```
